Structuration of Everest Bio Project

### 2022-02-14 data/Scopus/ES-Literature/ES-Literature.Rmd
presentation

Test <- CICES %>% select(Division, Group, Class, Code, `Class type`, `Simple descriptor`)
#write_yaml(V1, "GF/CICES-GF.yml")

# Ordering the Factors
Test <- Test %>%
  mutate(Division = factor(Division, Test %>% pull(Division) %>% unique())) %>% 
  mutate(Group = factor(Group, Test %>% pull(Group) %>% unique()))

Divisiones <- Test$Division %>% levels()
Grupos <- Test$Group %>% levels()

Total_preguntas <- Test %>% group_by(Division,Group) %>% tally()
#Encuesta <- list(Test$Division %>% levels())
```

>>>>

#CICES <- CICES %>% select(Filter, Section, Division, Group, Class, Code, `Class type`, `Simple descriptor`)

#Test <- tibble(CICES = Test %>% pull(Group) %>% unique())
#write_yaml(V1, "GF/CICES-GF.yml")

# Ordering the Factors
CICES <- 
  CICES %>%
  mutate(Section = factor(Section, CICES %>% pull(Section) %>% unique())) %>% 
  mutate(Division = factor(Division, CICES %>% pull(Division) %>% unique())) %>% 
  mutate(Group = factor(Group, CICES %>% pull(Group) %>% unique())) %>% 
  mutate(Section = 
           factor(Section, 
            c("Provisioning (Biotic)", "Provisioning (Abiotic)",
            "Regulation & Maintenance (Biotic)", "Regulation & Maintenance (Abiotic)",
            "Cultural (Biotic)", "Cultural (Abiotic)") ))

Cuestionario <- list()

Cuestionario$Industrial <- 
  CICES %>% group_by(Section,Group) %>% 
  tally()

CICES %>%
  filter(Code %in% c("1.1.1.1", "1.1.1.2", "1.1.1.3"))

# Identifying the codes
Test <- 
CICES %>%
  group_by(Group) %>%
  #arrange(stopSequence) %>%
  filter(row_number()==1 | row_number()==n())

library(readxl)
library(here)
library(flextable)

ft_1 <- flextable(data_ex)
ft_1 <- theme_box(ft_1)
ft_2 <- merge_v(ft_1, j = "srdr_id",
  target = c("srdr_id", "substances"))
  ft_2

CICES %>% select(Group, Class, Code) %>% 
  filter(Code %in% c("1.1.1.1", "1.1.1.2", "1.1.1.3")) %>% 
  flextable() %>% 
  merge_v( j = "Group")

  kbl(caption = "ES for Food Nutrition") %>%
  collapse_rows(columns = 1:1)

library(dplyr)
library(flextable)

devtools::install_github("haozhu233/kableExtra")

collapse_rows_dt <- data.frame(C1 = c(rep("a", 10), rep("b", 5)),
                 C2 = c(rep("c", 7), rep("d", 3), rep("c", 2), rep("d", 3)),
                 C3 = 1:15,
                 C4 = sample(c(0,1), 15, replace = TRUE))
kbl(collapse_rows_dt, align = "c") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "top")

Divisiones <- CICES$Division %>% levels()
Grupos <- Test$Group %>% levels()

Total_preguntas <- CICES %>% group_by(Section,Group) %>% tally()
#Encuesta <- list(Test$Division %>% levels())
```

### 2022-02-14 docs/PubliER/PPQS/PPQS.Rmd
presentation

---
title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
bibliography: library.bib
link-citations: yes
linkcolor: blue
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PPSQ

@@

>>>>

---
title: "Structuration of Everest Bio Project"
bibliography: "`r here::here('library.bib')`"
date: "`r paste('Last Version of the document: ', format(Sys.time(), '%b %d/%Y'))`"
fontsize: 12pt
link-citations: yes
linkcolor: blue
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Version I: Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing

@@

\newpage

# Version II  Fev 08/2022

<!-- Problem -->
The evaluation of the environmental externalities of (emergent) industrial systems in a territory is a central problem for decision-maker and industrial agents.
From an industrial perspective, techno-economical remains as the major and only criteria used to evaluate the feasibility of emergent industrial systems [in short circuit].
From a decision-maker perspective, a complete information about the relation on the impacts/dependencies of industrial systems on the natural capital and the ecosystems services of a particular territory is difficult to foreseen in the early/fuzzy-front design phases of development.
<!-- Knowledge Gap: Academic rational -->
In the scientific literature, life cycle thinking is a major body of knowledge to the quantification of the environmental impacts of industrial interventions, being Life cycle analysis a decision-aid tool for the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021]. 
Likewise, Ecosystem services have been a major conceptual framework in the evaluation of the natural capital and the valuation of supply/demand ES in a territory.
However, the research gap in the literature consist that few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
<!-- Purpose Statement: -->
The purpose of this research is to propose a methodological steps to identify the hotspot of ES in terms that converge in the industrial value chain and the territorial perspective.  
<!-- Research questions -->

\newpage
